Network based multifactorial modelling microRNA-target interaction.

### 2019-08-26 article.Rmd
re-scan to literature

>>>>

[#add]Similar with these approach, Silveira et al. have developed miRmapper package for using with R programme [@da2018mirmapper]. Researchers have utilized the adjacency matrix to associate miRNAs using differentially expressed genes and found similarities of miRNAs with this approach. Authors who utilized the approach in dataset of bladder cancer cell line have identified importance of miRNAs in network, and miRNAs which work synergistically.
